---
title: "Statistical Analysis for the Haptic Nudge Study"
author: "Usman Rashid, Alain C. Vandal"
date: "04/11/2019"
output:
  md_document:
    variant: gfm
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: true
    toc_depth: 4
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())

# function for is nan
is.nan.data.frame <- function(x)
  do.call(cbind, lapply(x, is.nan))
```

```{r data_setup, echo=FALSE, include=FALSE}

# Packages Used:
require(ggplot2)
require(lme4)
require(car)
require(MASS)
require(sjstats)
require(fBasics)
require(ggpubr)
require(reshape2)
require(phia)
require(emmeans)
require(multcomp)
require(jtools)
require(rsq)
require(r2glmm)
require(sjPlot)
require(MuMIn)
require(effects)
require(optimx)
require(margins)
require(cAIC4)
require(ggsignif)
require(nlme)
require(stringr)
require(dplyr)
require(forcats)
require(splines)
require(ggsci)
require(lemon)
require(data.table)

knit_print.data.frame <- lemon_print


# Load data
dataSource            <- read.csv("DataTable.csv", na.strings=c("","NA"))

# Exclude participant 2 and 6
dataSource$PartID     <- as.factor(dataSource$PartID)
dataSource$Time       <- as.factor(dataSource$Time)
dataSource$Obs        <- as.factor(dataSource$Obs)
dataSource$Logged_iPad<- as.factor(dataSource$Logged_iPad)
dataSource$Scheduled  <- as.factor(dataSource$Scheduled)

#dataSource            <- subset(dataSource, PartID != 2 & PartID != 6)

# Buzzed == NA is no
dataSource$Buzzed   <- factor(dataSource$Buzzed)
dataSource$Buzzed   <- as.character(dataSource$Buzzed)
dataSource$Buzzed[is.na(dataSource$Buzzed)] <- "n"
dataSource$Buzzed   <- tolower(dataSource$Buzzed)
dataSource$Buzzed   <- as.factor(dataSource$Buzzed)

# Remove spacing
dataSource$Reason_DNB <- tolower(str_squish(dataSource$Reason_DNB))
dataSource$Position <- tolower(str_squish(dataSource$Position))
dataSource$Not_Observed <- tolower(str_squish(dataSource$Not_Observed))
dataSource$Unable_To_Determine <- tolower(str_squish(dataSource$Unable_To_Determine))
dataSource$Move1 <- tolower(str_squish(dataSource$Move1))
dataSource$Move2 <- tolower(str_squish(dataSource$Move2))
dataSource$Move3 <- tolower(str_squish(dataSource$Move3))
dataSource$Move4 <- tolower(str_squish(dataSource$Move4))
dataSource$Move5 <- tolower(str_squish(dataSource$Move5))
dataSource$Move6 <- tolower(str_squish(dataSource$Move6))
dataSource$Where <- tolower(str_squish(dataSource$Where))
dataSource$With <- tolower(str_squish(dataSource$With))

# Make factors
dataSource$Reason_DNB <- as.factor(dataSource$Reason_DNB)
dataSource$Position <- as.factor(dataSource$Position)
dataSource$Not_Observed <- as.factor(dataSource$Not_Observed)
dataSource$Unable_To_Determine <- as.factor(dataSource$Unable_To_Determine)
dataSource$Where <- as.factor(dataSource$Where)
dataSource$With <- as.factor(dataSource$With)

# Melt Move Data
dataSource <- reshape2::melt(dataSource,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("PartID", "Time", "Obs", "Logged_iPad", "Scheduled", "Buzzed", "Reason_DNB", "Position", "Not_Observed", "Unable_To_Determine", "Where", "With"),
        # The source columns
    measure.vars=c("Move1", "Move2", "Move3", "Move4", "Move5", "Move6"),
        # Name of the destination column that will identify the original
        # column that the measurement came from
    variable.name="Move",
    value.name="Activity"
)

dataSource$Move <- as.factor(dataSource$Move)
dataSource$Activity <- as.factor(dataSource$Activity)

# Recode activity labels
levels(dataSource$Activity)[levels(dataSource$Activity) == "a" |
                              levels(dataSource$Activity) == "af"] <- "AU"
levels(dataSource$Activity)[levels(dataSource$Activity) == "ab" |
                              levels(dataSource$Activity) == "aub" |
                              levels(dataSource$Activity) == "b" |
                              levels(dataSource$Activity) == "baf" |
                              levels(dataSource$Activity) == "bau" |
                              levels(dataSource$Activity) == "bf" |
                              levels(dataSource$Activity) == "bu" |
                              levels(dataSource$Activity) == "uab" |
                              levels(dataSource$Activity) == "uaffb" |
                              levels(dataSource$Activity) == "ub" |
                              levels(dataSource$Activity) == "ubf"] <- "BiM"
levels(dataSource$Activity)[levels(dataSource$Activity) == "afu" |
                              levels(dataSource$Activity) == "afuf" |
                              levels(dataSource$Activity) == "au" |
                              levels(dataSource$Activity) == "auf" |
                              levels(dataSource$Activity) == "fua" |
                              levels(dataSource$Activity) == "ua" |
                              levels(dataSource$Activity) == "uaf" |
                              levels(dataSource$Activity) == "ufa" |
                              levels(dataSource$Activity) == "ufaf"] <- "BiL"
levels(dataSource$Activity)[levels(dataSource$Activity) == "n"] <- "No"
levels(dataSource$Activity)[levels(dataSource$Activity) == "u" |
                              levels(dataSource$Activity) == "uf"] <- "UU"
levels(dataSource$Activity)[levels(dataSource$Activity) == "unable to determine"] <- NA

dataSource$Hour <- as.factor(floor(as.numeric(dataSource$Obs) / 6.01) + 1)

dataSource$Activity <- relevel(dataSource$Activity, "No")

dataSource$Buzzed <- fct_relevel(dataSource$Buzzed, "n", "yes", "dnb", "bdi")
levels(dataSource$Buzzed)[levels(dataSource$Buzzed) == "n"] <- "No buzz"
levels(dataSource$Buzzed)[levels(dataSource$Buzzed) == "yes"] <- "Buzz"
levels(dataSource$Buzzed)[levels(dataSource$Buzzed) == "dnb"] <- "Did not buzz"
levels(dataSource$Buzzed)[levels(dataSource$Buzzed) == "bdi"] <- "Buzzed in error"

dataSource$Buzzed <- relevel(dataSource$Buzzed, "Buzz")

dataSource$Obs <- as.numeric(dataSource$Obs)

# Add Labels to With
levels(dataSource$With)[levels(dataSource$With) == "alone"] <- "Alone"
levels(dataSource$With)[levels(dataSource$With) == "doctor"] <- "Doctor"
levels(dataSource$With)[levels(dataSource$With) == "family"] <- "Family"
levels(dataSource$With)[levels(dataSource$With) == "nurse"] <- "Nurse"
levels(dataSource$With)[levels(dataSource$With) == "friend"] <- "Friend"
levels(dataSource$With)[levels(dataSource$With) == "health care assistant" |
                        levels(dataSource$With) ==  "healthcare assistant"] <- "Healthcare assistant"
levels(dataSource$With)[levels(dataSource$With) == "therapy assistant"] <- "Therapy assistant"
levels(dataSource$With)[levels(dataSource$With) == "therapist" |
                        levels(dataSource$With) == "physio"] <- "Therapist"
levels(dataSource$With)[levels(dataSource$With) == "family, doctor"] <- "Family:Doctor"
levels(dataSource$With)[levels(dataSource$With) == "family, friend"] <- "Family:Friend"
levels(dataSource$With)[levels(dataSource$With) == "family, health care assistant"] <- "Family:Healthcare assistant"
levels(dataSource$With)[levels(dataSource$With) == "family, therapist, hca"] <- "Family:Therapist:Healthcare assistant"
levels(dataSource$With)[levels(dataSource$With) == "family, nurse" |
                        levels(dataSource$With) == "nurse, family"] <- "Family:Nurse"
levels(dataSource$With)[levels(dataSource$With) == "family, therapist" |
                        levels(dataSource$With) == "therapist, family"] <- "Family:Therapist"
levels(dataSource$With)[levels(dataSource$With) == "healthcare assistant, nurse" |
                        levels(dataSource$With) == "nurse, healthcare assistant" |
                        levels(dataSource$With) ==  "nurse, health care assistant"] <- "Healthcare assistant:Nurse"
levels(dataSource$With)[levels(dataSource$With) == "other patients" |
                        levels(dataSource$With) == "other patients, breakfast group"] <- "Other patients"
levels(dataSource$With)[levels(dataSource$With) == "therapist, therapy assistant"] <- "Therapist:Therapy assistant"
levels(dataSource$With)[levels(dataSource$With) == "therapist, other patients"] <- "Therapist:Other patients"

dataSource$With <- fct_relevel(dataSource$With, "Alone", "Doctor", "Family", "Friend", "Nurse", 
                               "Other patients", "Therapist", "Therapy assistant", "Healthcare assistant", 
                               "Family:Doctor", "Family:Friend", "Family:Healthcare assistant", "Family:Nurse", 
                               "Family:Therapist", 
                               "Family:Therapist:Healthcare assistant", 
                               "Healthcare assistant:Nurse", "Therapist:Other patients",  "Therapist:Therapy assistant")

# Add Labels to Reason_DNB
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "accupuncture"] <- "Acupuncture"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "asleep" |
                         levels(dataSource$Reason_DNB) == "sleep" |
                         levels(dataSource$Reason_DNB) == "sleeping"] <- "Asleep"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "assessment"] <- "Assessment"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "bathroom"] <- "Bathroom"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "buzzed in error"] <- "Buzzed in error"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "couldn't locate"] <- "Couldn’t locate"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "curtain drawn" |
                         levels(dataSource$Reason_DNB) == "unable to buzz" |
                         levels(dataSource$Reason_DNB) == "curtain drawn" |
                         levels(dataSource$Reason_DNB) == "unable to see" |
                         levels(dataSource$Reason_DNB) == "curtains closed" |
                         levels(dataSource$Reason_DNB) == "curtains drawn" |
                         levels(dataSource$Reason_DNB) == "curatins closed"|
                         levels(dataSource$Reason_DNB) == "curtain drawn, unable to buzz" |
                         levels(dataSource$Reason_DNB) == "curtain drawn, unable to see" |
                         levels(dataSource$Reason_DNB) == "curtain closed,shower"] <- "Behind curtains"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "error" |
                         levels(dataSource$Reason_DNB) == "no data on acc" |
                         levels(dataSource$Reason_DNB) == "tech issue"] <- "Technical error"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "eathing/ drinking" |
                         levels(dataSource$Reason_DNB) == "eating" |
                         levels(dataSource$Reason_DNB) == "eating drinking" |
                         levels(dataSource$Reason_DNB) == "eating/ drinking"] <- "Eating/drinking"
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "not stated"] <- NA
levels(dataSource$Reason_DNB)[levels(dataSource$Reason_DNB) == "off ward"] <- "Off ward"

# Reason_DNB reduced
dataSource$Reason_DNB_reduced <- dataSource$Reason_DNB
levels(dataSource$Reason_DNB_reduced)[levels(dataSource$Reason_DNB_reduced) == "Asleep"] <- "Sleeping"
levels(dataSource$Reason_DNB_reduced)[levels(dataSource$Reason_DNB_reduced) == "Off ward" |
                         levels(dataSource$Reason_DNB_reduced) == "Behind curtains" |
                         levels(dataSource$Reason_DNB_reduced) == "Bathroom" |
                         levels(dataSource$Reason_DNB_reduced) == "Couldn’t locate"] <- "Unable to see"
levels(dataSource$Reason_DNB_reduced)[levels(dataSource$Reason_DNB_reduced) == "Eating/drinking" |
                         levels(dataSource$Reason_DNB_reduced) == "Assessment" |
                         levels(dataSource$Reason_DNB_reduced) == "Acupuncture" |
                         levels(dataSource$Reason_DNB_reduced) == "Couldn't locate"] <- "Inappropriate"
levels(dataSource$Reason_DNB_reduced)[levels(dataSource$Reason_DNB_reduced) == "dropout"] <- "Dropout"

# Add Labels to Where
levels(dataSource$Where)[levels(dataSource$Where) == "bathroom" |
                         levels(dataSource$Where) == "washroom"] <- "Bathroom"
levels(dataSource$Where)[levels(dataSource$Where) == "bed" |
                         levels(dataSource$Where) == "bedroom" |
                         levels(dataSource$Where) == "bedroom, bed" |
                         levels(dataSource$Where) == "bedroom, chair" |
                         levels(dataSource$Where) == "chair" |
                         levels(dataSource$Where) == "chair,bed" |
                         levels(dataSource$Where) == "room" |
                         levels(dataSource$Where) == "room, bed" |
                         levels(dataSource$Where) == "wheelchair"] <- "Bedroom"
levels(dataSource$Where)[levels(dataSource$Where) == "bed to toilet" |
                         levels(dataSource$Where) == "bed, bathroom" |
                         levels(dataSource$Where) == "bedroom, bathroom"  ] <- "Bedroom:Bathroom"
levels(dataSource$Where)[levels(dataSource$Where) == "bed, rehab ward, gym"] <- "Bedroom:Ward:Gym"
levels(dataSource$Where)[levels(dataSource$Where) == "dining room"] <- "Dining room"
levels(dataSource$Where)[levels(dataSource$Where) == "garden"] <- "Garden"
levels(dataSource$Where)[levels(dataSource$Where) == "gym"] <- "Gym"
levels(dataSource$Where)[levels(dataSource$Where) == "kitchen"] <- "Kitchen"
levels(dataSource$Where)[levels(dataSource$Where) == "lift" |
                         levels(dataSource$Where) == "off ward"] <- "Off ward"
levels(dataSource$Where)[levels(dataSource$Where) == "lounge"] <- "Lounge"
levels(dataSource$Where)[levels(dataSource$Where) == "rehab ward"] <- "Rehab ward"
levels(dataSource$Where)[levels(dataSource$Where) == "cafe"] <- "Cafe"

# Make move continuous
dataSource$Move <- as.numeric(dataSource$Move)

# Remove Buzzed in error
#dataSource <- subset(dataSource, Buzzed != "Buzzed in error")

# Remove variables which are not included in the report
dataSource$Where <- NULL
dataSource$With <- NULL
dataSource$Logged_iPad <- NULL
dataSource$Scheduled <- NULL
dataSource$Position <- NULL
dataSource$Not_Observed <- NULL
dataSource$Unable_To_Determine <- NULL
dataSource$Reason_DNB <- dataSource$Reason_DNB_reduced
dataSource$Reason_DNB_reduced <- NULL

# Additional Cleanup
dataSource$Reason_DNB <- fct_explicit_na(dataSource$Reason_DNB, na_level = "Not stated")
dataSource$Activity <- fct_explicit_na(dataSource$Activity, na_level = "Not recorded")
dataSource$Activity <- fct_relevel(dataSource$Activity, "AU", "BiL", "BiM", "UU", "No", "Not recorded")

dataSource$Reason.DNN <- dataSource$Reason_DNB
dataSource$Reason_DNB <- NULL

dataSource <- droplevels(dataSource)

# Relabel categories
dataSource$Buzzed <- factor(dataSource$Buzzed, levels = c("Buzz", "No buzz", "Did not buzz", "Buzzed in error"),
                            labels = c("Nudged", "Not nudged", "Missed nudge", "Nudged in error"))
dataSource$Nudge.Status <- dataSource$Buzzed
dataSource$Buzzed <- NULL
dataSource.withMove <- dataSource
dataSource$Move <- NULL

# Load Rand Schedule
randSchedule <- read.csv("RandSchedule.csv")
#randSchedule <- randSchedule[-c(2,6),]
```

\newpage

# Randomisation Schedule

Haptic nudge reminders were manually triggered by the observer immediately prior to movement observation by the researcher according to a planned randomisation schedule, such that for half of the observation periods a haptic nudge was to be provided and for half a haptic nudge was not to be provided. To account for any potential carry over effect across multiple observation periods randomisation was designed to deliver different types of nudge sequences. These sequences are given in the following table along with their number of occurrences.

```{r rand_seq, echo=FALSE, warning=TRUE, render=lemon_print}
tNudges <- matrix(nrow = 20, ncol = 3)
nNudges <- matrix(nrow = 20, ncol = 3)

for(i in seq(1, 20)) {
  vec <- as.numeric(randSchedule[i,])
  vec.a <- as.numeric(unlist(by(vec, rleid(vec), cumsum)))
  vec.b <- -1*(vec - 1)
  vec.b <- as.numeric(unlist(by(vec.b, rleid(vec.b), cumsum)))
  
  tNudges[i, 3] <- sum(vec.a == 3)
  tNudges[i, 2] <- sum(vec.a == 2) - tNudges[i, 3]
  tNudges[i, 1] <- sum(vec.a == 1) - tNudges[i, 2] - tNudges[i, 3]
  
  nNudges[i, 3] <- sum(vec.b == 3)
  nNudges[i, 2] <- sum(vec.b == 2) - nNudges[i, 3]
  nNudges[i, 1] <- sum(vec.b == 1) - nNudges[i, 2] - nNudges[i, 3]
}


textNudge <- c("Nudge, No nudge", "Nudge-Nudge, No nudge-No nudge", "Nudge-Nudge-Nudge, No nudge-No nudge-No nudge", "Total")

nudgeData <- c("120, 120", "120, 120", "120, 120",  "720, 720")

d <- data.frame(textNudge, nudgeData)
names(d) <- c("Nudge sequence", "No. of occurrences")

head(d)
```

# Variables Included in the Analysis

```{r summary_stats, echo=FALSE}
str(dataSource)
```

\newpage

# Data Visualisations

## Activity Distribution

```{r act_dist, echo=FALSE, warning=TRUE}
ggplot(data = dataSource, aes(x=Nudge.Status, y=reorder(Activity, desc(Activity)), color = Activity)) + geom_jitter(size=0.7) + 
  scale_color_nejm() + scale_fill_nejm() + theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) + ylab("Activity") + xlab('Nudge status')
```

\newpage

## Activity Proportions

Each planned category (Nudge, No nudge) was to precede half (or 50%) of the total observations. However, it was not always possible to nudge the participants in accordance with the schedule. This resulted in an additional category (Missed nudge). Moreover, in some cases participants were nudged mistakenly when they were not supposed to be nudged. This also resulted in an additional category (Nudged in error).

```{r act_prop, echo=FALSE, warning=TRUE}
sData <- as.data.frame(dataSource %>% group_by(Nudge.Status, Activity) %>% summarise(Count = n() / (6*72*20) * 100, .groups="drop_last"))
ggplot() + geom_bar(data=sData, aes(x = Nudge.Status, y=Count, fill=Activity), position="stack", stat="identity") +
  scale_color_nejm() + scale_fill_nejm() + theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) + ylab('Proportion of total observations (%)') + xlab('Nudge status') +
  scale_y_continuous(breaks=seq(0, 50, 5), limits = c(0, 50))
```

## Reasons for Missed Nudges

```{r rsn_dnb, echo=FALSE, warning=TRUE}
dataSource_dnb <- subset(dataSource, Nudge.Status == "Missed nudge")
dataSource_dnb$Activity <- factor(dataSource_dnb$Activity, levels = c("No", "AU", "BiM", "BiL", "UU", "Not recorded"), 
                                     labels = c("No", "AU, BiL, BiM", "AU, BiL, BiM", "AU, BiL, BiM", "No", "Not recorded"))
dataSource_dnb$Activity <- fct_relevel(dataSource_dnb$Activity, "AU, BiL, BiM", "No", "Not recorded")
sData <- as.data.frame(dataSource_dnb %>% group_by(Reason.DNN, Activity) %>% summarise(Count = n() /(3*72*20) * 100, .groups="drop_last"))
sData$Reason.DNN <- fct_relevel(sData$Reason.DNN, "Sleeping", "Dropout", "Unable to see", "Inappropriate", "Technical error", "Not stated")
ggplot(data=sData, aes(x = Reason.DNN, y=Count, fill=Activity)) + geom_bar(stat = 'identity') + scale_color_nejm() + scale_fill_nejm() + theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=8)) + ylab('Proportion of planned nudges (%)') + xlab('Reasons for missed nudges') +
   scale_y_continuous(breaks=seq(0, 15, 1), limits = c(0, 15))
```
\newpage

## Participant-wise Activity Proportions

In this and subsequent sections, Nudged and Missed nudge are treated as a single category (Planned nudge), and Not nudged and Nudged in error are both treated as No nudge.

```{r buzz_vs_no_buzz, echo=FALSE, warning=TRUE}
dataSource.orig <- dataSource
dataSource$Nudge.Status <- factor(dataSource$Nudge.Status, levels = c("Nudged", "Not nudged", "Missed nudge", "Nudged in error"),
                            labels = c("Planned nudge", "No nudge", "Planned nudge", "No nudge"))
dataSource_buzzed <- dataSource
tData <- as.data.frame(dataSource_buzzed %>% group_by(Activity, Nudge.Status) %>% summarise(per = n() / (3*72*20) * 100, .groups="drop_last"))
sData <- as.data.frame(dataSource_buzzed %>% group_by(PartID, Activity, Nudge.Status) %>% summarise(per = n() / (3*72) * 100, .groups="drop_last"))
sData$Activity <- fct_relevel(sData$Activity, "AU", "BiL", "BiM", "UU", "No", "Not recorded")
tData$Activity <- fct_relevel(tData$Activity, "AU", "BiL", "BiM", "UU", "No", "Not recorded")

sData <- subset(sData, Activity != "Not recorded")
sData <- subset(sData, Activity != "No")

tData <- subset(tData, Activity != "Not recorded")
tData <- subset(tData, Activity != "No")

sData$Nudge.Status <- fct_relevel(sData$Nudge.Status, "No nudge", "Planned nudge")
tData$Nudge.Status <- fct_relevel(tData$Nudge.Status, "No nudge", "Planned nudge")

tData$PartID <- "All"

sData <- rbind(sData, tData)

ggplot() + geom_bar(data=sData, aes(x = PartID, y=per, fill=Activity), position="stack", stat="identity", width = 0.7)  +
facet_wrap(~Nudge.Status, nrow = 2, ncol = 1) +
ylab('Proportion of observations following No nudge, Planned nudge (%)') + xlab('Participant') +
scale_color_nejm() + scale_fill_nejm() + theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) + scale_y_continuous(breaks=seq(0, 100, 10), limits = c(0, 100), sec.axis =
                       sec_axis(~., name = "Proportion of observations following No nudge, Planned nudge (%)", breaks=seq(0, 100, 10)))
```
\newpage

## Participant-wise Proportions for AU, BiL, BiM

```{r buzz_vs_no_buzzII, echo=FALSE, warning=TRUE}
sData <- subset(sData, Activity == "AU" | Activity == "BiL" | Activity == "BiM")
sData$PartID <- reorder(sData$PartID, desc(sData$PartID))
sData <- droplevels(sData)
sData$Activity <- factor(sData$Activity,
                             levels = c("AU", "BiL", "BiM"),
                             labels = c("AU, BiL, BiM", "AU, BiL, BiM", "AU, BiL, BiM"))
sData <- droplevels(sData)

sData.small <- sData[sData$PartID != 'All',]

sData.small <- as.data.frame(sData.small %>% group_by(PartID, Nudge.Status) %>% summarise(t=sum(per), .groups="drop_last"))

temp.a<-sData.small[sData.small$PartID == 3 & sData.small$Nudge.Status == 'Planned nudge',]
temp.b<-temp.a
temp.a$PartID<-2
temp.a$t<-0

temp.b$PartID<-6
temp.b$t<-0

sData.small <- rbind(sData.small, temp.a)
sData.small <- rbind(sData.small, temp.b)

sData.small$Nudge.Schedule <- sData.small$Nudge.Status

ggplot() + geom_bar(data=sData.small, aes(x = PartID, y=t, fill=Nudge.Schedule), position="stack", stat="identity", width = 0.7)  + ylab('Proportion of observations following No nudge, Planned nudge (%)') + xlab('Participant') + facet_wrap(~Nudge.Schedule) + coord_flip() +
  scale_color_nejm() + scale_fill_nejm() + theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))

# For publication
#ggplot() + geom_bar(data=sData.small, aes(x = PartID:fct_rev(Buzzed), y=t, fill=Buzzed), position="stack", stat="identity", width = 0.7)  + ylab('Proportion of observations following no nudge, planned nudge (%)') + xlab('Participant') + coord_flip() +
#  scale_color_nejm() + scale_fill_nejm() + theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
```
\newpage

# Primary Analysis

The aim of this intention to treat analysis is to estimate the effect of Planned nudge compared to No nudge on the combined proportion of AU, BiL or BiM types of activity out of AU, BiL, BiM, UU and No.

```{r mdl_data_prep, echo=TRUE, include=TRUE, warning=TRUE}
modelData                 <- dataSource.orig

modelData$Nudge.Schedule  <- factor(modelData$Nudge.Status,
                                    levels = c("Nudged", "Not nudged",
                                               "Missed nudge", "Nudged in error"),
                                    labels = c("Planned nudge", "No nudge",
                                               "Planned nudge", "No nudge"))

modelData$Activity        <- factor(modelData$Activity,
                                    levels = c("AU", "BiL", "BiM", "UU",
                                               "No", "Not recorded"),
                                    labels = c("AU, BiL, BiM", "AU, BiL, BiM",
                                               "AU, BiL, BiM",
                                               "No", "No", "Not recorded"))

levels(modelData$Activity)[levels(modelData$Activity) == "Not recorded"] <- NA

modelData$Activity        <- relevel(modelData$Activity, "No")
```

## Logistic Mixed Model

The model has smooth cubic splines to explain variance across time. The knots are placed at: [8:00 AM, 9:00 AM, 10:00 AM, 11:00 AM, 12:00 PM, 1:00 PM, 2:00 PM, 3:00 PM, 4:00 PM, 5:00 PM, 6:00 PM].

```{r model_setup_sens, echo=TRUE, include=TRUE, warning=TRUE}
lmerModel <- glmer(Activity ~ Nudge.Schedule + ns(Obs, knots = seq(7, 67, 6)) +
                     (1|PartID/Hour),
                   na.action = na.omit,
                   data = modelData,
                   family = binomial(link = "logit"),
                   control = glmerControl(optimizer = "bobyqa"))
```

## Model Estimates with Confidence Intervals

```{r mdl_estim, include=TRUE, echo=FALSE, warning=TRUE, render=lemon_print}
a<-data.frame(emmeans(lmerModel, ~Nudge.Schedule, type = "response"))
a$df <- NULL
colnames(a) <- c("Buzzed", "Probability", "SE", "95% CI lower", "95% CI upper")
head(a)

pa <- pairs(emmeans(lmerModel, ~Nudge.Schedule, type = "response"))
co <- as.data.frame(confint(pa))
co$null <- NULL
co <- co[,c(5,6)]
pa <- as.data.frame(pa)
pa$null <- NULL

estims <- cbind(pa, co)
estims$df <- NULL
colnames(estims) <- c("Contrast", "Odds ratio", "SE", "Z-value", "P-value", "95% CI lower", "95% CI upper")

head(estims)
```

\newpage

## Variance Explained across Time with Natural Splines

```{r mdl_ns, include=TRUE, echo=FALSE, warning=TRUE}
emipData <- emmip(lmerModel, Nudge.Schedule~Obs, CIs = TRUE, type = "response",
                  cov.reduce = FALSE, at = list(Obs=seq(1, 72)),
                  plotit = FALSE)

tLabels <- dataSource$Time
tLabels <- tLabels[seq(1, 72)]

emipData$Nudge.Schedule <- fct_relevel(emipData$Nudge.Schedule, "No nudge", "Planned nudge")

ggplot(data=emipData, aes(x=Obs, y=yvar, color=Nudge.Schedule)) +
  geom_line() + 
  geom_ribbon(aes(ymax=UCL, ymin=LCL, fill=Nudge.Schedule, color=NULL), alpha=0.15) +
  scale_color_nejm() + scale_fill_nejm() + theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  scale_x_continuous(breaks = c(seq(1, 72, 12), 72), labels = tLabels[c(seq(1, 72, 12), 72)]) +
  xlab('Time of the day') + ylab('Probability of AU, BiL or BiM')
```
\newpage

## Sensitivity Analysis

A sensitivity analysis consisting of a simulated worst-case scenario is conducted to evaluate the sensitivity of the estimated effect size for the Planned nudge to missing data. The worst-case simulation is based on multiple (m = 10) random imputations from single trial binomial distributions with mean activity proportions of the participant with worst outcomes.

```{r mdl_data_prep_sens, echo=TRUE, include=TRUE, warning=TRUE}
modelData.WC              <- dataSource.orig

modelData.WC$
  Nudge.Schedule          <- factor(modelData.WC$Nudge.Status,
                                    levels = c("Nudged", "Not nudged",
                                               "Missed nudge", "Nudged in error"),
                                    labels = c("Planned nudge", "No nudge",
                                               "Planned nudge", "No nudge"))

modelData.WC$Activity     <- factor(modelData.WC$Activity,
                                    levels = c("AU", "BiL", "BiM", "UU",
                                               "No", "Not recorded"),
                                    labels = c("AU, BiL, BiM", "AU, BiL, BiM",
                                               "AU, BiL, BiM",
                                               "No", "No", "Not recorded"))

levels(modelData.WC$Activity)[levels(modelData.WC$Activity) == "Not recorded"] <- NA

modelData.WC$Activity     <- relevel(modelData.WC$Activity, "No")

list.modelData.WC         <- list()

for(i in seq(1, 10)) { # 10 random imputations
  
  freshCopy               <- modelData.WC
  
  # Random imputation
  # Number of missing values following "No nudge"       = 542
  rNN                     <- factor(rbinom(542, 1, 6.4814815/100),
                                    levels = c(0, 1), labels = c("No", "AU, BiL, BiM"))
  # Number of missing values following "Planned nudge"  = 1122 - 542
  rPN                     <- factor(rbinom(1122 - 542, 1, 0.9259259/100),
                                    levels = c(0, 1), labels = c("No", "AU, BiL, BiM"))
  
  freshCopy$Activity[is.na(freshCopy$Activity) &
                       freshCopy$Nudge.Schedule == "No nudge"]      <- rNN
  freshCopy$Activity[is.na(freshCopy$Activity) &
                       freshCopy$Nudge.Schedule == "Planned nudge"] <- rPN
  
  list.modelData.WC[[i]]  <- freshCopy
}
```

\newpage

### Logistic Mixed Models

```{r model_setup, echo=TRUE, include=TRUE, warning=TRUE}
list.lmerModel.WC <- list()
for(i in seq(1, 10)) {
  list.lmerModel.WC[[i]] <- glmer(Activity ~ Nudge.Schedule +
                                    ns(Obs, knots = seq(7, 67, 6)) +
                                    (1|PartID/Hour),
                                  na.action = na.omit,
                                  data = list.modelData.WC[[i]],
                                  family = binomial(link = "logit"),
                                  control = glmerControl(optimizer = "bobyqa"))
}
```

###  Sensitivity Estimates with Confidence Intervals

```{r mdl_estim_sens, include=TRUE, echo=FALSE, warning=FALSE, render=lemon_print}
list.a.IV <- list()
list.estims.IV <- list()
for(i in seq(1, 10)) {
a<-data.frame(emmeans(list.lmerModel.WC[[i]], ~Nudge.Schedule, type = "response"))
a$df <- NULL
colnames(a) <- c("Nudge.Schedule", "Probability", "SE", "95% CI lower", "95% CI upper")
a$Case <- "WC"
a.IV <- a

a.IV <- a.IV[, c(6, 1,2,3,4,5)]

list.a.IV[[i]] <- a.IV

pa <- pairs(emmeans(list.lmerModel.WC[[i]], ~Nudge.Schedule, type = "response"))
co <- as.data.frame(confint(pa))
co$null <- NULL
co <- co[,c(5,6)]
pa <- as.data.frame(pa)
pa$null <- NULL

estims <- cbind(pa, co)
estims$df <- NULL
colnames(estims) <- c("Contrast", "Odds ratio", "SE", "Z-value", "P-value", "95% CI lower", "95% CI upper")

estims$Case <- "WC"

estims.IV <- estims

estims.IV <- estims.IV[, c(8, seq(1,7))]

list.estims.IV[[i]] <- estims.IV
}

t.a<-do.call("rbind", list.a.IV)
t.a<-as.data.frame(t.a %>% group_by(Case, Nudge.Schedule) %>% summarise(Probability = mean(Probability), SE=mean(SE), `95% CI lower`=mean(`95% CI lower`), `95% CI upper`=mean(`95% CI upper`), .groups = "drop_last"))
head(t.a)

t<-do.call("rbind", list.estims.IV)
t<-as.data.frame(t %>% group_by(Case, Contrast) %>% summarise(`Odds ratio` = mean(`Odds ratio`), SE=mean(SE), `Z-value` = mean(`Z-value`), `P-value` = mean(`P-value`), `95% CI lower`=mean(`95% CI lower`), `95% CI upper`=mean(`95% CI upper`), .groups = "drop_last"))
head(t)
```

\newpage

## Exploratory Analysis

### Local Average Treatment Effect (LATE)

To estimate the local average treatment effect (also known as complier average causal effect (CACE)), an instrumental variable analysis is conducted.

```{r mdl_data_prep_sens_late, echo=TRUE, include=TRUE, warning=TRUE}
modelData.IV                <- dataSource.orig

modelData.IV$
  Nudge.Schedule            <- factor(modelData.IV$Nudge.Status,
                                      levels = c("Nudged", "Not nudged",
                                                 "Missed nudge", "Nudged in error"),
                                      labels = c("Planned nudge", "No nudge",
                                                 "Planned nudge", "No nudge"))

modelData.IV$Nudge.Schedule <- relevel(modelData.IV$Nudge.Schedule, "No nudge")

modelData.IV$Nudge.Deliver  <- factor(modelData.IV$Nudge.Status,
                                      levels = c("Nudged", "Not nudged",
                                                 "Missed nudge", "Nudged in error"),
                                      labels = c("Nudged", "Not nudged",
                                                 "Not nudged", "Nudged"))

modelData.IV$Activity       <- factor(modelData.IV$Activity,
                                      levels = c("AU", "BiL", "BiM", "UU", "No",
                                                 "Not recorded"),
                                      labels = c("AU, BiL, BiM", "AU, BiL, BiM",
                                                 "AU, BiL, BiM",
                                                 "No", "No", "Not recorded"))
modelData.IV$Activity       <- relevel(modelData.IV$Activity, "No")

levels(modelData.IV$Activity)[levels(modelData.IV$Activity) == "Not recorded"] <- NA
```

### Logistic Mixed Models

```{r model_setup_LATE, echo=TRUE, include=TRUE, warning=TRUE}
lmerModel.IV.r        <- glmer(Nudge.Deliver ~ ns(Obs, knots = seq(7, 67, 6))*Nudge.Schedule +
                                 (1|PartID/Hour),
                               family = binomial(link="logit"),
                               modelData.IV,
                               control = glmerControl(optimizer = "bobyqa",
                                                      optCtrl=list(maxfun = 1e6)))

modelData.IV$
  Nudge.Schedule.r    <- resid(lmerModel.IV.r, type = "response")

lmerModel.IV          <- glmer(Activity ~ Nudge.Deliver + Nudge.Schedule.r +
                                 ns(Obs, knots = seq(7, 67, 6)) +
                                 (1|PartID/Hour),
                               na.action = na.omit,
                               data = modelData.IV,
                               family = binomial(link = "logit"),
                               control = glmerControl(optimizer = "bobyqa"))
```

\newpage

###  LATE Estimate with Confidence Intervals

```{r mdl_estim_sens_LATE, include=TRUE, echo=FALSE, warning=TRUE, render=lemon_print}
a<-data.frame(emmeans(lmerModel.IV, ~Nudge.Deliver, type = "response"))
a$df <- NULL
colnames(a) <- c("Buzzed", "Probability", "SE", "95% CI lower", "95% CI upper")
a$Case <- "LATE"
a.IV <- a

a.IV <- a.IV[, c(6, 1,2,3,4,5)]

head(a.IV)

pa <- pairs(emmeans(lmerModel.IV, ~Nudge.Deliver, type = "response"))
co <- as.data.frame(confint(pa))
co$null <- NULL
co <- co[,c(5,6)]
pa <- as.data.frame(pa)
pa$null <- NULL

estims <- cbind(pa, co)
estims$df <- NULL
colnames(estims) <- c("Contrast", "Odds ratio", "SE", "Z-value", "P-value", "95% CI lower", "95% CI upper")

estims$Case <- "LATE"

estims.IV <- estims

estims.IV <- estims.IV[, c(8, seq(1,7))]

head(estims.IV)
```

### Estimated Compliance across Time

```{r mdl_ns_compliance, include=TRUE, echo=FALSE, warning=FALSE}
modelData.IV.c <- modelData.IV

modelData.IV.c$Nudge.Deliver   <- relevel(modelData.IV.c$Nudge.Deliver, "Not nudged")

lmerModel.IV.r.c        <- glmer(Nudge.Deliver ~ ns(Obs, knots = seq(7, 67, 6))*Nudge.Schedule +
                                 (1|PartID/Hour),
                               family = binomial(link="logit"),
                               modelData.IV.c,
                               control = glmerControl(optimizer = "bobyqa",
                                                      optCtrl=list(maxfun = 1e6)))


emipData <- emmip(lmerModel.IV.r.c, Nudge.Schedule~Obs, CIs = FALSE, type = "response",
                  cov.reduce = FALSE, at = list(Obs=seq(1, 72)),
                  plotit = FALSE)

tLabels <- dataSource$Time
tLabels <- tLabels[seq(1, 72)]

ggplot(data=emipData, aes(x=Obs, y=yvar, color=Nudge.Schedule)) +
  geom_line() +
  scale_color_nejm() + scale_fill_nejm() + theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  scale_x_continuous(breaks = c(seq(1, 72, 12), 72), labels = tLabels[c(seq(1, 72, 12), 72)]) +
  xlab('Time of the day') + ylab('Probability of Nudged')
```

\newpage

# Secondary Analysis

The aim of this analysis is to separately estimate the effect of Planned nudge compared to No nudge on the proportion of AU and BiL or BiM types of activity out of AU, BiL, BiM, UU and No.

## Logistic Mixed Models

Two linear logistic mixed regression models are setup to separately estimate the effect of Planned nudge compared to No nudge on AU and BiL or BiM.

```{r mdl_fit_sec, echo=TRUE, include=TRUE, warning=TRUE}
# Model for AU
modelData_AU              <- dataSource.orig

modelData_AU$
  Nudge.Schedule          <- factor(modelData_AU$Nudge.Status,
                                    levels = c("Nudged", "Not nudged",
                                               "Missed nudge", "Nudged in error"),
                                    labels = c("Planned nudge", "No nudge",
                                               "Planned nudge", "No nudge"))

modelData_AU$Activity     <- factor(modelData_AU$Activity,
                             levels = c("AU", "BiL", "BiM", "UU",
                                        "No", "Not recorded"),
                             labels = c("AU", "No", "No",
                                        "No", "No", "Not recorded"))

levels(modelData_AU$Activity)[levels(modelData_AU$Activity) == "Not recorded"] <- NA

modelData_AU$Activity     <- relevel(modelData_AU$Activity, "No")

lmerModel_AU              <- glmer(Activity ~ Nudge.Schedule +
                                     ns(Obs, knots = seq(7, 67, 6)) +
                                     (1|PartID/Hour),
                                   na.action = na.omit,
                                   data = modelData_AU,
                                   family = binomial(link = "logit"),
                                   control = glmerControl(optimizer = "bobyqa"))

# Model for BiL, BiM
modelData_BiL_BiM         <- dataSource.orig

modelData_BiL_BiM$
  Nudge.Schedule          <- factor(modelData_BiL_BiM$Nudge.Status,
                                    levels = c("Nudged", "Not nudged",
                                               "Missed nudge", "Nudged in error"),
                                    labels = c("Planned nudge", "No nudge",
                                               "Planned nudge", "No nudge"))

modelData_BiL_BiM$
  Activity                <- factor(modelData_BiL_BiM$Activity,
                                    levels = c("AU", "BiL", "BiM", "UU",
                                               "No", "Not recorded"),
                                    labels = c("No", "BiL, BiM", "BiL, BiM",
                                               "No", "No", "Not recorded"))

levels(modelData_BiL_BiM$Activity)[levels(modelData_BiL_BiM$Activity) == "Not recorded"] <- NA

modelData_BiL_BiM$
  Activity                <- relevel(modelData_BiL_BiM$Activity, "No")

lmerModel_BiL_BiM         <- glmer(Activity ~ Nudge.Schedule +
                                     ns(Obs, knots = seq(7, 67, 6)) +
                                     (1|PartID/Hour),
                                   na.action = na.omit,
                                   data = modelData_BiL_BiM,
                                   family = binomial(link = "logit"),
                                   control = glmerControl(optimizer = "bobyqa"))
```


## Model Estimates with Confidence Intervals

```{r mdl_estim_sec, include=TRUE, echo=FALSE, warning=TRUE, render=lemon_print}
pa_AU <- pairs(emmeans(lmerModel_AU, ~Nudge.Schedule, type = "response"))
co_AU <- as.data.frame(confint(pa_AU))
co_AU$null <- NULL
co_AU <- co_AU[,c(5,6)]
pa_AU <- as.data.frame(pa_AU)
pa_AU$null <- NULL

estims_AU <- cbind(pa_AU, co_AU)
estims_AU$df <- NULL
estims_AU$contrast <- "Planned nudge / No nudge (AU)"

pa_BiL_BiM <- pairs(emmeans(lmerModel_BiL_BiM, ~Nudge.Schedule, type = "response"))
co_BiL_BiM <- as.data.frame(confint(pa_BiL_BiM))
co_BiL_BiM$null <- NULL
co_BiL_BiM <- co_BiL_BiM[,c(5,6)]
pa_BiL_BiM <- as.data.frame(pa_BiL_BiM)
pa_BiL_BiM$null <- NULL

estims_BiL_BiM <- cbind(pa_BiL_BiM, co_BiL_BiM)
estims_BiL_BiM$df <- NULL
estims_BiL_BiM$contrast <- "Planned nudge / No nudge (BiL or BiM)"

estims <- rbind(estims_AU, estims_BiL_BiM)

colnames(estims) <- c("Contrast", "Odds ratio", "SE", "Z-value", "P-value", "95% CI lower", "95% CI upper")

head(estims[, c(1,2,3,4,5)])
head(estims[, c(1,6,7)])
```